---
title: "Airport data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Airport data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The airport data in the **flightsbr** package is downloaded from Brazil’s Civil Aviation Agency (ANAC).

- Airports data cover all airports and aerodromes registered in Brazil’s Civil Aviation Agency (ANAC).  It covers detailed information on....[mention a few key variables].

Data dictionary: the data dictionary for public airports can be found at \url{https://www.anac.gov.br/acesso-a-informacao/dados-abertos/areas-de-atuacao/aerodromos/lista-de-aerodromos-publicos-v2/70-lista-de-aerodromos-publicos-v2}. The data dictionary for private airports can be found at \url{https://www.anac.gov.br/acesso-a-informacao/dados-abertos/areas-de-atuacao/aerodromos/lista-de-aerodromos-privados-v2}.

Now we can load some libraries we'll use in this vignette:

```{r, eval=FALSE, message=FALSE}
library(flightsbr)
library(dplyr)
library(data.table)
library(ggplot2)
# library(geobr)

```

Download data of all airports:

```{r, eval=FALSE, message=FALSE}
# download data
airports_priv <- flightsbr::read_airports(type = 'private', showProgress = FALSE)
airports_publ <- flightsbr::read_airports(type = 'public', showProgress = FALSE)

# change col names to lower case
names(airports_priv) <- tolower(names(airports_priv))
names(airports_publ) <- tolower(names(airports_publ))

# select columns
cols_to_keep <- c('ciad','nome', 'longitude', 'latitude')
airports_publ <- select(airports_publ, cols_to_keep)
airports_priv <- select(airports_priv, cols_to_keep)

# rbind all public and private airports
airports <- data.table::rbindlist(list(airports_priv,airports_publ), fill = T)


# plot
# brazil <- geobr::read_country()

ggplot() +
  # geom_sf(data=brazil, color='gray') +
  geom_point(data=airports, aes(x=longitude, y=latitude), size=.5 , alpha=.4) +
  theme_void()
```


