---
title: "Flights data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Flights data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The flight data in the **flightsbr** package is downloaded from Brazil’s Civil Aviation Agency (ANAC). The data includes detailed information on every international flight to and from Brazil, as well as domestic flights within the country. The data include flight-level information of airports of origin and destination, flight duration, aircraft  type, payload, and the number of passengers, and several other variables. 

A description of all variables included in the data is available at \url{https://www.anac.gov.br/assuntos/setor-regulado/empresas/envio-de-informacoes/descricao-de-variaveis}.



Now we can load some libraries we'll use in this vignette:

```{r, message = FALSE}
library(flightsbr)
library(ggplot2)
library(dplyr)
library(data.table)

```

Download data of all flights:

```{r, eval=FALSE}
# in a given **month* of a given **year** (yyyymm)
df_201506 <- read_flights(date=201506, showProgress = FALSE)

# in a given year (yyyy)
df_2015 <- read_flights(date=2015, showProgress = FALSE)

```


If you know already what data columns you need, you can pass a vector with their names to `select` parameter and `read_flights()` will only load those columns. This will make the function a bit faster. 

```{r, eval=TRUE}
df_201506 <- read_flights(date=201506, 
                          showProgress = FALSE,
                          select = c('id_empresa', 'nr_voo', 'dt_partida_real',
                                     'sg_iata_origem' , 'sg_iata_destino'))

head(df_201506)
```

The package makes it easy to compare daily number of passengers across different years.


```{r, eval=TRUE}
df_2019 <- read_flights(date=2019, showProgress = TRUE)
df_2020 <- read_flights(date=2020, showProgress = TRUE)
```

