---
title: "Introduction to flightsbr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to flightsbr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

**flightsbr** is an R package to download flight data from Brazil’s Civil Aviation Agency (ANAC). The data includes detailed information on every international flight to and from Brazil, as well as domestic flights within the country. The data include flight-level information of airports of origin and destination, flight duration, aircraft  type, payload, and the number of passengers, and several other variables. 

A description of all variables included in the data is available at \url{https://www.anac.gov.br/assuntos/setor-regulado/empresas/envio-de-informacoes/descricao-de-variaveis}.


# Basic usage

Before using **flightsbr** please make sure that you have it installed on your computer. You can download either the most stable version from CRAN...

```{r, eval = FALSE}
install.packages("flightsbr")
```

...or the development version from GitHub.

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("ipeaGIT/flightsbr")
```

Then attach it to the current R session:

```{r, message = FALSE}
library(flightsbr)
```

Download data

```{r}
df201506 <- read_flights(year=2015, month=6)

head(df201506)
```
