---
title: "Introduction to flightsbr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to flightsbr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

**flightsbr** is an R package to download flight and airport data from Brazil’s Civil Aviation Agency (ANAC). The package currently includes five main functions:

1. `read_flights()`
2. `read_airports()`
3. `read_aircrafts()`
4. `read_airport_movements()`
5. `read_airfares()`

### 1) `read_flights()`:
Flights data include detailed information on every international flight to and from Brazil, as well as domestic flights within the country. The data include flight-level information of airports of origin and destination, flight duration, aircraft  type, payload, and the number of passengers, and several other variables. 
- [Data dictionary for flights](https://www.gov.br/anac/pt-br/assuntos/regulados/empresas-aereas/Instrucoes-para-a-elaboracao-e-apresentacao-das-demonstracoes-contabeis/descricao-de-variaveis).


### 2) `read_airports()`
Airports data covers all airports and aerodromes registered in Brazil’s Civil Aviation Agency (ANAC).  It covers detailed information on ICAO code, municipality, geographical coordinates, runway dimensions etc.

- Data dictionary: 
  - [Public airports](https://www.anac.gov.br/acesso-a-informacao/dados-abertos/areas-de-atuacao/aerodromos/lista-de-aerodromos-publicos-v2/70-lista-de-aerodromos-publicos-v2).
  - [Private airports](https://www.anac.gov.br/acesso-a-informacao/dados-abertos/areas-de-atuacao/aerodromos/lista-de-aerodromos-privados-v2).

### 3) `read_aircrafts()`:
All aircrafts registered in the Brazilian Aeronautical Registry (Registro Aeronáutico Brasileiro - RAB), organized by the Brazilian Civil Aviation Agency (ANAC).
- [Data dictionary for aircrafts data](https://dados.gov.br/dataset/aeronaves-registradas-no-registro-aeronautico-brasileiro-rab).


### 4) `read_airport_movements()`:
The data covers all passenger, aircraft, cargo and mail movement from airports regulated by ANAC.
- [Data dictionary for airport movements data](https://www.anac.gov.br/acesso-a-informacao/dados-abertos/areas-de-atuacao/operador-aeroportuario/operador-aeroportuario-dados-de-movimentacao-aeroportuaria/metadados-do-conjunto-de-dados-dados-de-movimentacao-aeroportuaria).



### 5) `read_airfares()`:
The data covers airfares of domestic and international flights.

- Data dictionary: 
  - [domestic airfares](https://www.anac.gov.br/acesso-a-informacao/dados-abertos/areas-de-atuacao/voos-e-operacoes-aereas/tarifas-aereas-domesticas/46-tarifas-aereas-domesticas).
  - [international airfares](https://www.gov.br/anac/pt-br/assuntos/dados-e-estatisticas/microdados-de-tarifas-aereas-comercializadas).



## Basic usage

Before using **flightsbr** please make sure that you have it installed on your computer. You can download the most stable version from CRAN.

```{r, eval = FALSE}
install.packages("flightsbr")
```

Now we can load the library and start downloading data.

```{r, eval=FALSE}
library(flightsbr)
```

#### Download flights data:

```{r, eval=FALSE}
# in a given **month* of a given **year** (yyyymm)
df_201506 <- read_flights(date=201506, showProgress = FALSE)

# in a given year (yyyy)
df_2015 <- read_flights(date=2015, showProgress = FALSE)

```

#### Download airports data:

```{r, eval=FALSE}
airports_all <- flightsbr::read_airports(type = 'all', showProgress = FALSE)

airports_prv <- flightsbr::read_airports(type = 'private', showProgress = FALSE)

airports_pbl <- flightsbr::read_airports(type = 'public', showProgress = FALSE)


```


#### Download data of aircrafts:

```{r, eval=FALSE}
aircrafts <- flightsbr::read_aircrafts(showProgress = FALSE)

head(aircrafts)
```



#### Download data on airport movements:

```{r, eval=FALSE}
airport_mov <- flightsbr::read_airport_movements(date=201901)

head(airport_mov)
```



#### Download data on data on air fares of domestic flights in Brazil:

```{r, eval=FALSE}
air_fares <- flightsbr::read_airfares(date=202003)

head(air_fares)
```

