---
title: "Introduction to flightsbr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to flightsbr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

**flightsbr** is an R package to download flight and airport data from Brazil’s Civil Aviation Agency (ANAC). The package currently includes two main functions:

### `read_flights()`:
- Flights data include detailed information on every international flight to and from Brazil, as well as domestic flights within the country. The data include flight-level information of airports of origin and destination, flight duration, aircraft  type, payload, and the number of passengers, and several other variables. 

Data dictionary: a description of all variables included in the data is available at \url{https://www.anac.gov.br/assuntos/setor-regulado/empresas/envio-de-informacoes/descricao-de-variaveis}.

### `read_airports()`
- Airports data covers all airports and aerodromes registered in Brazil’s Civil Aviation Agency (ANAC).  It covers detailed information on....[mention a few key variables].

Data dictionary: the data dictionary for public airports can be found at \url{https://www.anac.gov.br/acesso-a-informacao/dados-abertos/areas-de-atuacao/aerodromos/lista-de-aerodromos-publicos-v2/70-lista-de-aerodromos-publicos-v2}. The data dictionary for private airports can be found at \url{https://www.anac.gov.br/acesso-a-informacao/dados-abertos/areas-de-atuacao/aerodromos/lista-de-aerodromos-privados-v2}.


## Basic usage

Before using **flightsbr** please make sure that you have it installed on your computer. You can download the most stable version from CRAN.

```{r, eval = FALSE}
install.packages("flightsbr")
```

Now we can load some libraries we'll use in this vignette:

```{r, message = FALSE}
library(flightsbr)
```

#### Download data of flights:

```{r, eval=FALSE}
# in a given **month* of a given **year** (yyyymm)
df_201506 <- read_flights(date=201506, showProgress = FALSE)

# in a given year (yyyy)
df_2015 <- read_flights(date=2015, showProgress = FALSE)

```

#### Download data of airports:

```{r, eval=FALSE}
airports_all <- flightsbr::read_airports(type = 'all', showProgress = FALSE)
airports_prv <- flightsbr::read_airports(type = 'private', showProgress = FALSE)
airports_pbl <- flightsbr::read_airports(type = 'public', showProgress = FALSE)

head(airports_all, width =2)
```


